---
title: "My C.V."
---

```{r echo = FALSE, warning=FALSE}
library(tinytex)
suppressPackageStartupMessages(library(icons))

```

## Hi there!

## Teaching Experience

**Math and Biology Teacher** \[2015 - 2019\] \| Accra Community School - Ghana

## Education

-   **PhD in Chemical Biology** \[2021 - *currently*\[ \| University of Grenoble Alpes
    -   EDyP Lab - CEA Grenoble
    -   Project: I use mass spectrometry (MS) technique to analyze histone post-translational modifications (hPTMs) in the context of Huntington's Disease.
-   **Master 2 in NanoBiology** \[2021\] \| University of Grenoble Alpes
    -   6-month internship: Impact of detergents on sequencing membrane proteins using MALDI-MS
    -   Institut de Biologie Structurale (IBS) - Grenoble/France
-   **Master 2 in Systems and Synthetic Biology** \[2020\] \| University of Paris Saclay
    -   6-month internship: Ultradeep Sequence-Function Mapping of Prokaryotic Promoter Libraries
    -   Department of Biosystems Science and Engineering (D-BSSE) - ETH - Basel/Switzerland
-   **Master 1 Animal Biology** \[2014\] \| Lebanese Univeristy
-   **BS in Life & Earth Sciences** \[2013\] \| University of Paris Saclay

## Computational Skills

-   Programming languages: R, Python

-   Graphics software: Inkscape

-   Writing: $\LaTeX$

## Languages

-   English (Fluent)

-   French (Intermediate)

-   Arabic (Native)

Thanks for dropping by! Find can find me also on:

```{r echo = FALSE}
fontawesome(name = 'linkedin')
```

[LinkedIn](https://www.linkedin.com/in/hijaziihassan/)

```{r echo = FALSE}
fontawesome(name = 'twitter')
```

[Twitter](https://x.com/HassanHejazi)

```{r echo = FALSE}
academicons(name = 'orcid')
```

[orcid](https://orcid.org/my-orcid?orcid=0000-0001-6408-1768)
